At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families - Supporting Information

### 2019-11-30 manuscript/reply_to_referees_2.tex

\begin{letter}{\bf Dr. Jana Vamosi\\
               Editor\\
               Proceedings of the Royal Society B\\
               6-9 Carlton House Terrace\\
               London, UK\\
               SW1Y 5AG\\
                }

\opening{Dear Dr. Vamosi:}

	We are pleased to submit a revised version of our manuscript, NPH-MS-2019-30803. In response to a suggestion from Referee 3, we have re-titled it "". We have also taken care to revise our methods section in response to the many helpful suggestions from Referee 4, and hope that our approach is now clearer. Finally, we have expanded the discussion to include some additional concepts suggested by Referees 2 and 4, and a possible application of our research suggested by Referee 3.

	Given the difference of opinion between Referees 1, 3, and 4 and Referee 2, we have prioritised adjusting the manuscript according to the majority view. We must also admit to having some difficulty parsing a number of Referee 2's comments in order to find what is being asked. This may be partly because this review came from several people - the Referee refers to themselves as 'we' several times, and the writing appears to be more than usually variable within their comments. These difficulties mean that we may not have followed as many of Referee 2's suggestions as we have for the other Referees. Nevertheless, we do appreciate their time and effort in offering such extensive feedback and have taken care to address each of Referee 2's comments in the hope of at least clarifying our perspective.

	We appreciate all of the Referees' comments and are confident that our manuscript is all the stronger for responding to them.

@@

	\smallskip

	In what follows we share with authors our specific comments expecting that they will help to re-think the manuscript and get a stronger contribution.

	\end{refquote}

	The Referee(s?) seems to view our basic question and analyses positively, but is rather bluntly critical of our writing in terms of logical, clarity, and style. Some of these criticisms seem to reflect a rather hasty reading of the manuscript, as there are points where the Referee asks for analyses or ideas to be included which already appear in the text. In these cases, we point to existing evidence in the manuscript and have tried to make these connections more obvious. In a few cases, we struggled to understand the nature of the Referee's objections. We have attempted to address each of the Referee's comments in detail below (preceded by \textbf{R:}). Wherever possible, we have clarified our text in response to the Referee's comments. In particular, we now define community composition more explicitly, have revised the discussion to be more explicit about whether we are referring to overall or within-network trends, and have removed specific phrases that the Referee finds objectionable \emph{prima facie}. We hope that these changes and our response will clarify the focus and scope of our analyses.

	1. General criticism of the language of the text

@@

		\begin{refquote}

		Finally, the text needs English revision by the authors as we feel that some ideas are not clearly stated because of the way they are presented to readers.

		\end{refquote}

		\textbf{R:} As Referees 1 and 3 note, our English is scrupulously correct. Of course technical correctness does not necessarily imply clarity of expression, and we apologise if our choice of vocabulary has obfuscated some of the nuances of the manuscript. We have endeavoured to clarify the manuscript as the Referee suggests.

	2. Title lacks clarity

		\begin{refquote}
		Specific comments\\
		Title\\
		Your title still lacks clarity and does not reflect the main message you state at the beginning of your discussion (in the first sentence of it you state that you found broad support for the hypothesis that more closely related plants tend to have more niche overlap). We feel that this reflects lack of logical consistency across your manuscript, so re-thinking it should help to define your title.
		\end{refquote}

@@

		\textbf{R:} We have revised the title following a more detailed suggestion by Referee 3 and hope that the new title no longer implies logical inconsistency.

	3. Summary too methodologically-oriented in general

		\begin{refquote}
			Summary\\
			General comments\\
			Your summary is too methodologically-oriented. In fact, when we were invited to be reviewers of your manuscript and received your abstract we thought that your paper represented a methodological contribution and it is not. After reading the comments that former reviewers sent you, your abstract seems to correspond to an older version of your manuscript. The thing is that by presenting an abstract that is methodologically-oriented when in fact you are not innovating in this sense, and having an introduction and a discussion that lack such methodological issue and are clearly more biologically-oriented can be read as that your work lacks focus.
		\end{refquote}

@@

		\begin{refquote}
			Your 2nd paragraph is too technical: which is the biological meaning of it? Why are you going to compare pollination and herbivory networks? Why your datasets are so unbalanced? Why are you considering a wide range of pollination networks and a narrow one for herbivory networks? Why you consider shared and unshared partners? Your first point in the abstract doesn't introduce a methodological problem to be solve. (...) "and whether this relationship varies with the composition of the plant community"? What does it mean?
		\end{refquote}

		\textbf{R:} We regret that the Referee finds our summary too methodologically-orientated, but note that Referee 4 has requested that we include further methodological details in the summary. Moreover, in a later comment this Referee also requests more methodological details. To balance these conflicting comments, we no longer emphasise the methodological novelty of our study but have added the greater detail requested. As the other three Referees for this revision did not find the summary overly methodological in its original form, we are confident that the revised summary does not indicate that we lack focus. We also note that the extremely tight word limit for the summary does not allow us to explain why we have unbalanced numbers of pollination and herbivory networks. This information is contained in the methods.

	4. Mis-understanding of purpose and scope of within-family analyses

@@

		\begin{refquote}
		Your abstract also evidences your confusion with phylogenetic issues and taxonomic ones. For instance, your hypothesis is that more closely related plants will share more pollinators and herbivores than less closely related. Then, why searching for different relationships within families? This decision is completely arbitrary is one of the weakest point of the manuscript in general.
		\end{refquote}

		\textbf{R:} The Referee is correct about our hypothesis but appears to have assumed that we are \emph{only} searching for conservation of niche overlap within families. In fact, point 2 of the summary lists three separate analyses: testing for relationships between phylogenetic distance and partner overlap in \emph{all pairs of plants in a network, regardless of family}, testing whether the slopes of these whole-network relationships are related to the composition of the plant community in each network, and, as a supplement to these analyses, testing whether the slopes of these relationships differ if we consider only pairs of plants within the same family. We now number these three different analyses to avoid any further confusion.

		In this context, checking for different relationships within families is similar to checking for different relationships between networks - an overall trend can mask a great deal of variability, and we wanted to make sure this variability was identified. We chose families as the taxonomic level for further analysis because many plant families are quite diverse, both in terms of numbers of species and in terms of phenotypes/interaction partners (see e.g., Wilson on plants and insect/bird pollinators). Within a single family, plants can show evidence of adaptive radiations, heterogeneous selection, both, or neither. The Referee themself points out that some families can show both bird and bee pollination syndromes (see response \#8), and we can also point to papers such as Bernhardt 2000 and Johnson \& Jurgens 2010 which address trait lability, convergent evolution, and adaptive radiation. These different possibilities mean that it is not clear whether all families will show phylogenetic conservation of interaction partners. 
		We have added a summary of this explanation to the methods.

@@

		\begin{refquote}
			Line 318. Within-family conservation of niche overlap. Your result is almost expected so we think is important to justify biologically why you decided to look at the family level.
		\end{refquote}

	5. Very confusing comment complaining about summary point 4

		\begin{refquote}
		4st paragraph "Considering factors affecting the dominant plant families within
		a community may be the key to understanding the distribution of interactions." So, relationships are more functional? Why focusing on plant families? we are not sure the logic of your thoughts can be followed (can the reader reach this conclusion? is it ok? we mean, if there are other eco-evolutionary processes determining species interactions why focusing in the dominant plant families would be informative? I feel the way this last paragraph is written isn't clear enough and is your main paragraph.
		\end{refquote}

		\textbf{R:} Apart from the Referee's objection to plant families as units for detailed analysis (see respons \#4), this comment seems to demonstrate uncertainty about how we defined the dominant plant families in a community. Note that we do not mean to imply any functional argument here, as our manuscript does not address functionality. Rather, by 'dominant', we mean 'most species-rich in the focal community'. In order to avoid future confusion, we now replace 'dominant families' with 'species-rich groups'. We hope that this makes it clear that we are advocating researcher take a finer-scale perspective on phylogenetic signal in ecological networks.

@@

		\begin{quotation}
		    \item The variety of relationships between phylogenetic distance and partner overlap in different plant families likely reflects a comparable variety of ecological and evolutionary processes. Considering factors affecting particular species-rich groups within a community may be the key to understanding the distribution of interactions.
		\end{quotation}

	6. Complaint about keywords absent from the abstract

		\begin{refquote}
		Keywords\\
		Syndrome:  Why you do not mention such theory in your abstract?
		\end{refquote}

		\textbf{R:} The abstract/summary is under strict word limits, and we did not feel that inserting each keyword without a clear purpose could justify the elimination of other material. Given the Referee's confusion regarding our analyses, we are more convinced than ever that our decision to omit some keywords in favour of spending more words explaining our methodology was correct. As we do not directly test pollination or defensive syndromes, we have removed these keywords from the list. In response to the Referee's further objections to the syndrome literature, below, we have also removed these terms from the introduction.

	7. Mistake about the focus of the introduction

		\begin{refquote}
		Introduction\\
		General. You focus on the compromise between pollination and herbivory interactions but then you do not use this approach in your analyses.
		\end{refquote}

		\textbf{R:} Potential tradeoffs between encouraging interactions with pollinators and discouraging herbivores are just one of the possible reasons why networks may not display the expected relationship between relatedness and niche overlap. Note that we also propose several others in the same paragraph where trade-offs appear, including convergent evolution or selection to avoid pollen dilution. We therefore disagree with the Referee's perception that we focus on compromise between pollination and herbivory. It is beyond the scope of this manuscript to test all possible reasons why closely-related plants might not share interaction partners. This material is intended solely as background for readers who may not be familiar with arguments against the phylogenetic conservation of interaction partners.

	8. Disagreement with any link between syndromes and conservation of interaction partners

@@

		\begin{refquote}
			2nd paragraph: your reasoning is not clear for us. Syndromes imply the convergence of phenotypic traits into one common set of traits because of their functionality in increasing fitness (because of the selection pressures imposed by functional groups of pollinators that can or cannot be closely related). Even if traits are heritable, if many unrelated groups converge into one functional group of interaction partners, why you may expect more similarity among closely related species? On the other hand, can we expect modular structures based on your reasoning? Then, how you explain the high incidence of nested structures in both mutualistic and antagonistic networks? In fact, what has been proposed for coevolution in mutualistic networks is the convergence of species traits to those of the species forming the core (see Guimaraes et al 2017, Nuismer et al. 2018). In antagonistic networks your line of reasoning may apply, but this will clearly depend on the intimacy of your network as most herbivory networks tend to show nested structures too. Your reasoning is based on pairwise coevolution and does not incorporate ideas of evolution and coevolution in networks, which may completely alter your predictions about niche overlap.
		\end{refquote}

		\begin{refquote}
			Lines 65-65. You wrote: Unrelated plants might also converge upon similar phenotypes, attracting a particularly efficient or abundant pollinator (Ollerton, 1996; Wilson et al., 2007; Ollerton et al., 2009; Ibanez et al., 2016). This is exactly our point: pollination syndromes may reflect trait convergence among unrelated species.
		\end{refquote}

		\textbf{R:} As the Referee notes, we do address the possibility of convergence in our introduction. We do not make any claim as to whether the putative pollination syndromes actually reflect plants with common sets of pollinators (the evidence we are aware of is rather mixed). Since the Referee appears to object to this idea (which we note is quite common in the literature surrounding phylogenetic conservation of interactions), and because syndromes do not form a major part of our analysis, we have removed it as a keyword and rephrased our introduction so that it now no longer references pollination syndromes. Hopefully this will help readers to take our manuscript on its own merits rather than those of the syndrome concept.

@@

		\end{quotation}

	9. Request to include interaction intimacy

		\begin{refquote}
		Lines 35-39. Maybe you should use the idea of interaction intimacy, since it clearly will determine the level of selective pressure landscape perceived by a given species?
		\end{refquote}

		\textbf{R:} We have no information on interaction strengths or intimacies, and we note that the interactions we consider are generally low-intimacy. We therefore would not expect intimacy to strongly affect these networks. However, we are happy to include the idea as yet another reason why plant communities may or may not show conservation of interactions. We have added a brief description of intimacy as follows:

@@

			In mutualistic networks, animals often show a stronger phylogenetic signal in their partners than do plants~\citep{Rezende2007a,Chamberlain2014,Rohr2014,Vamosi2014,Lind2015,Fontaine2015} (but see~\citet{Rafferty2013} for a counterexample). In antagonistic networks, however, actively-foraging consumers tend to show less phylogenetic signal than their prey~\citep{Ives2006,Cagnolo2011,Naisbit2011,Fontaine2015}. In part, this may be related to different degrees of interaction intimacy (dependence of one partner on another), which appears to contribute to network structure in mutualistic, but not antagonistic, networks~\citep{Guimaraes2007,Ponisio2017}.

		\end{quotation}

		In addition to the above, we have added another brief discussion of intimacy in the discussion (see response \#28)

	10. Criticism of dataset changes required by previous reviewers

		\begin{refquote}
		Methods\\
		Dataset\\
		Several networks can be reviewed in the literature or are available in different websites. Why authors decide not to consider several plant-herbivore networks but have no filter to separate plant-pollinator networks? The reason of why focusing in plant-pollinator and plant-herbivory networks is not clear for us as well why authors choose to select just one kind of herbivory interaction and as a consequence have a highly unbalanced design. Such decision seems to be crucial as it may modulate the results and conclusions they achieve. By eliminating the herbivory interactions that are more phylogenetically constrained their result that pollination interactions may be more conserved than herbivory interactions seems to be a by-product of such decision.
		\end{refquote}

		\textbf{R:} We included all herbivory networks we could find when we began this project, and only restricted our selection of herbivory networks in response to a previous round of review. Without more details why (or if) the Referee believes that the herbivory networks we removed should be included, we have opted to continue following that earlier feedback. We would have appreciated specific tips for additional herbivory networks, but since the Referee does not provide any specifics we do not feel that conducting an extensive search for additional networks and repeating our analyses is viable within the timeframe given to respond to this review.

	11. Request to change "insects consuming leaves" to "chewing insects"

@@

		\begin{refquote}
			Lines 93 to 96. We think that sap-sucking, leaf mining, and galling insects are also insect consuming leaves. Maybe you could change "insect consuming leaves" by "chewing insects"
		\end{refquote}

		\textbf{R:} The term "insects consuming leaves" was recommended by an earlier reviewer, but we agree that leaf mining also constitutes leaf consumption (this is not necessarily the case for sap-sucking and galling, which is less leaf-specific). We have changed these lines as suggested.

	12. Recommendation to continue using Jaccard dissimilarity, binomial regression

		\begin{refquote}
			Measuring niche overlap\\
			Why you used absolute numbers to measure shared and unshared pollinators and not the Jaccard index? Or, instead, why you did not use a binomial regression considering the absolute number of the whole set of pollinators that can be shared ? You should use generalized linear models with a binomial distribution considering the total number of pollinators and shared pollinators to give more weight to those species sharing more pollinators in a larger sample (generalists s for instance). It is not clear for us if your analysis considers the full number of species over which you obtain the percentage of shared species.
		\end{refquote}

		\textbf{R:} We did use a Jaccard index, as stated in the first  sentence under the sub-heading \textbf{Calculating niche overlap between communities} in the previous revision. This line read as follows (emphasis added): 
		\begin{quotation}
		We calculated niche overlap for each pair of species within a community \emph{using a Jaccard index} to describe the number of shared interaction partners, augmented with the number of interaction partners which were not shared.
		\end{quotation}

		The Jaccard index is calculated using the number of shared and un-shared interaction partners for a pair of plants, as stated in equation 1. We also did use a generalised linear model with binomial error distribution, as stated in the \textbf{Statistical analysis} section. We chose this methodology for exactly the reasons the Referee suggests, to give more weight to generalists sharing many interaction partners. This is stated in lines 138-141 and lines 148-154 (quoted below). Note that we have revised these lines somewhat in response to a suggestion from Referee 4, so they do differ somewhat from the previous version. We are glad that the Referee agrees with our choice in methodology.

@@

		\begin{quotation}

			We modelled the relationship between niche overlap and phylogenetic 
			distance using a logistic regression. We used the numbers of shared 
			($M_{ij}$) and non-shared ($U_{ij}$) partners as dependent variables and 
			centred, scaled phylogenetic distance as the independent variable. This 
			approach is conceptually similar to modelling successes and failures in a 
			binomial-distributed process. Accordingly, we assumed a binomially-distributed error structure and used a logit link function to model the dissimilarity in interaction partners 
			$J_{ij}$ of plants $i$ and $j$.

		\end{quotation}

		As stated in the section on phylogenetic data, we excluded comparisons involving plants for which we could not assign a binomial names (and therefore could not obtain phylogenetic distances) and comparisons between non-angiosperms due to our coarse estimates of their ages. This information appeared in lines 107-110 and 118-120 of the previous version and lines 112-115 and 122-124 of the current version.

	13. Request to include plant species as a fixed effect

@@

		\begin{refquote}
			176-178. Why you do not consider using plant species as another fixed factor to break the lack of independence? This is because generalist species may have more weight in your analyses than other species. It would be interesting to see how your results differ from an analysis considering such approach.
		\end{refquote}

		\textbf{R:} It sounds as though the Referee would like us to include plant species as a predictor in our regressions. Due to the fact that species generally appear in few networks (many in only a single network), this would result in near singularity of our models. We would therefore be completely unable to observe any patterns as species identity would explain nearly all variation in niche overlap. If the Referee is referring to a potential effect of network size, we did in fact test this (see equation 4 and description). If the Referee did not mean either of these possibilities, we apologise but are unable to understand this comment.

	14. Request to include connectance

@@

		\begin{refquote}
			198-209. Why did you decide to control just for network size and do not consider network connectance? You provide methodological information to explain your decision but there is no biological argument explaining why network size may influence the relationship between phylogenetic relatedness and niche overlap.
		\end{refquote}

		\textbf{R:} Our main reason for including network size as a potential effect was methodological rather than biological - slopes for smaller networks are based on smaller sample sizes and therefore may be less robust. We do not see either the methodological or biological arguments for including connectance as a predictor. We also note that the manuscript is already quite full, so including these new analyses would require us to remove something more important. Without a justification from the Referee as to why connectance should affect pairwise niche overlap, we have opted not to add this new thread to the manuscript.

	15. Confusion about motivation for community composition analyses

@@

		\begin{refquote}
			Line 210 Linking network level trends and community composition

### 2019-12-05 manuscript/supporting_info.tex
checked all refs

\section*{Supporting information 1: Sources for networks}
  \begin{table}[!h]
    \caption{Original sources for each network used in our analyses. All networks beginning 'M\_PL\_' were collected from~\citet{weboflife}. Further details for unpublished networks may be found there.}
    \label{sources}
    \begin{center}
    \begin{tabular}{|l l l m{8cm} |}
    \hline
    Network & Network type & Country & Original source  \\
    \hline
    M\_PL\_001  & Pollination & Chile & \citep{Arroyo1982}  \\
    M\_PL\_002  & Pollination & Chile & \citep{Arroyo1982}  \\
    M\_PL\_003  & Pollination & Chile & \citep{Arroyo1982}  \\
    M\_PL\_004  & Pollination & Canada (New Brunswick) & \citep{Barrett1987} \\
    M\_PL\_005  & Pollination & U.S.A. (Colorado) & \citep{Clements1923}  \\
    M\_PL\_006  & Pollination & U.K. (Norfolk) & \citep{Dicks2002} \\
    M\_PL\_007  & Pollination & U.K. (Norfolk) & \citep{Dicks2002} \\
    M\_PL\_008  & Pollination & Spain (Canary Islands) & \citep{Dupont2003}  \\
    M\_PL\_009  & Pollination & Sweden & \citep{Elberling1999} \\
    M\_PL\_010  & Pollination & Denmark (Greenland) & Elberling, H. \& Olesen, J. M. Unpub. \\
    M\_PL\_011  & Pollination & Mauritius & \citep{Olesen2002a}  \\
    M\_PL\_012  & Pollination & Portugal (Azores) & \citep{Olesen2002a}  \\
    M\_PL\_013  & Pollination & South Africa (KwaZulu-Natal) & \citep{Ollerton2003}  \\
    M\_PL\_014  & Pollination & Canada (N.W.T.) & \citep{Hocking1968} \\
    M\_PL\_015  & Pollination & Greece (Athens) & \citep{Petanidou1991} \\
    M\_PL\_016  & Pollination & Spain (Andalucia) & \citep{Herrera1988} \\
    M\_PL\_017  & Pollination & U.K. (England) & \citep{Memmott2002} \\
    M\_PL\_018  & Pollination & Denmark & Olesen, J. M. Unpublished.  \\
    M\_PL\_019  & Pollination & U.S.A. (Colorado) & \citep{Inouye1988}  \\
    M\_PL\_020  & Pollination & Canada (N.W.T.) & \citep{Kevan1970} \\
    M\_PL\_021  & Pollination & Japan (Kyoto) & \citep{Kato1990}  \\
    M\_PL\_022  & Pollination & Argentina (Mendoza) & \citep{Medan2002} \\
    M\_PL\_023  & Pollination & Argentina (Mendoza) & \citep{Medan2002} \\
    M\_PL\_024  & Pollination & Canada (N.W.T.) & \citep{Mosquin1967} \\
    M\_PL\_025  & Pollination & U.S.A. (North Carolina) & \citep{Motten1982}  \\
    M\_PL\_026  & Pollination & Ecuador (Gal\'{a}pagos Islands) & \citep{McMullen1993}  \\
    M\_PL\_027  & Pollination & New Zealand (South Island) & \citep{Primack1983} \\
    M\_PL\_028  & Pollination & New Zealand (South Island) & \citep{Primack1983} \\
    M\_PL\_029  & Pollination & New Zealand (South Island) & \citep{Primack1983} \\
    M\_PL\_030  & Pollination & Venezuela & \citep{Ramirez1992} \\
    M\_PL\_031  & Pollination & Venezuela & \citep{Ramirez1989} \\
    \hline
    \end{tabular}
    \end{center}
    \end{table}

@@

    \begin{table*}[h!]
    \begin{center}
    \begin{tabular}{|l l l m{6cm} |}
    \hline
    Network & Network type & Country & Original source \\
    \hline
    M\_PL\_032  & Pollination & U.S.A. (Illinois) & \citep{Schemske1978}  \\
    M\_PL\_033  & Pollination & Canada (Ontario) & \citep{Small1976} \\
    M\_PL\_034  & Pollination & Chile & \citep{SmithRamirez2005}  \\
    M\_PL\_035  & Pollination & Jamaica & \citep{Percival1974}  \\
    M\_PL\_036  & Pollination & Portugal (Azores) & Olesen, J. M. Unpublished.  \\
    M\_PL\_037  & Pollination & Denmark & \citep{Montero2005} \\
    M\_PL\_038  & Pollination & Denmark & \citep{Montero2005} \\
    M\_PL\_039  & Pollination & Spain (Canary Islands) & \citep{Stald2003} \\
    M\_PL\_040  & Pollination & Jamaica & \citep{Ingversen2006} \\
    M\_PL\_041  & Pollination & Dominica & \citep{Ingversen2006} \\
    M\_PL\_042  & Pollination & Ecuador (Gal\'{a}pagos Islands) & \citep{Philipp2006} \\
    M\_PL\_043  & Pollination & Denmark & \citep{Montero2005} \\
    M\_PL\_044  & Pollination & Japan (Amami Islands) & \citep{Kato2000}  \\
    M\_PL\_045  & Pollination & Denmark (Greenland) & \citep{Lundgren2005}  \\
    M\_PL\_046  & Pollination & Denmark & \citep{Bundgaard2003} \\
    M\_PL\_047  & Pollination & Denmark & \citep{Dupont2009a}  \\
    M\_PL\_048  & Pollination & Denmark & \citep{Dupont2009a}  \\
    M\_PL\_049  & Pollination & Denmark & \citep{Bek2006}  \\
    M\_PL\_050  & Pollination & Spain (Canary Islands) & \citep{Stald2003} \\
    M\_PL\_051  & Pollination & Argentina (R\'{i}o Negro) & \citep{Vazquez2002} \\
    M\_PL\_052  & Pollination & Denmark (Greenland) & \citep{Witt1998}  \\
    M\_PL\_053  & Pollination & Japan (Kyusu) & \citep{Yamazaki2003}  \\
    M\_PL\_054  & Pollination & Japan (Kyoto) & \citep{Kakutani1990}  \\
    M\_PL\_055  & Pollination & Japan (Fukui Prefacture) & \citep{Kato1996}  \\
    M\_PL\_056  & Pollination & Japan (Yamanashi) & \citep{Kato1993}  \\
    M\_PL\_057  & Pollination & Japan (Kibune) & \citep{Inoue1990} \\
    M\_PL\_058  & Pollination & Spain (Catalonia) & \citep{Bartomeus2008} \\
    M\_PL\_059  & Pollination & Brazil (Bu\'{i}que) & \citep{Bezerra2009} \\
    Basset  & Herbivory & Papua New Guinea & \citep{Basset1996}  \\
    Bl\"{u}thgen  & Herbivory & Malaysia (Sabah) & \citep{Bluthgen2006a}  \\
    Bodner  & Herbivory & Ecuador & \citep{Bodner2010}  \\
    Coley & Herbivory & Panama & \citep{Coley2006} \\
    Ibanez  & Herbivory & France (Central French Alps) & \citep{Ibanez2013}  \\
    Joern\_altuda  & Herbivory & U.S.A. (Texas) & \citep{Joern1979} \\
    Joern\_marathon  & Herbivory & U.S.A. (Texas) & \citep{Joern1979} \\
    Novotny & Herbivory & Papua New Guinea & \citep{Novotny2012} \\
    Peralta & Herbivory & New Zealand (South Island) & \citep{Peralta2016} \\
    Sheldon & Herbivory & U.S.A. (Washington) & \citep{Sheldon1978} \\
    Ueckert & Herbivory & U.S.A. (Colorado) & \citep{Ueckert1971} \\
    \hline
    \end{tabular}
    \end{center}
    \end{table*}
\clearpage
\newpage

>>>>

\section*{Supporting information 1: Sources for networks}
  \begin{table}[!h]
    \caption{Original sources for each network used in our analyses. All networks beginning 'M\_PL\_' were collected from~\citet{weboflife}. Further details for unpublished networks may be found there.}
    \label{sources}
    \begin{center}
    \begin{tabular}{|l l l m{8cm} |}
    \hline
    Network & Network type & Country & Original source  \\
    \hline
    M\_PL\_001  & Pollination & Chile & \citet{Arroyo1982}  \\
    M\_PL\_002  & Pollination & Chile & \citet{Arroyo1982}  \\
    M\_PL\_003  & Pollination & Chile & \citet{Arroyo1982}  \\
    M\_PL\_004  & Pollination & Canada (New Brunswick) & \citet{Barrett1987} \\
    M\_PL\_005  & Pollination & U.S.A. (Colorado) & \citet{Clements1923}  \\
    M\_PL\_006  & Pollination & U.K. (Norfolk) & \citet{Dicks2002} \\
    M\_PL\_007  & Pollination & U.K. (Norfolk) & \citet{Dicks2002} \\
    M\_PL\_008  & Pollination & Spain (Canary Islands) & \citet{Dupont2003}  \\
    M\_PL\_009  & Pollination & Sweden & \citet{Elberling1999} \\
    M\_PL\_010  & Pollination & Denmark (Greenland) & Elberling, H. \& Olesen, J. M. Unpub. \\
    M\_PL\_011  & Pollination & Mauritius & \citet{Olesen2002a}  \\
    M\_PL\_012  & Pollination & Portugal (Azores) & \citet{Olesen2002a}  \\
    M\_PL\_013  & Pollination & South Africa (KwaZulu-Natal) & \citet{Ollerton2003}  \\
    M\_PL\_014  & Pollination & Canada (N.W.T.) & \citet{Hocking1968} \\
    M\_PL\_015  & Pollination & Greece (Athens) & \citet{Petanidou1991} \\
    M\_PL\_016  & Pollination & Spain (Andalucia) & \citet{Herrera1988} \\
    M\_PL\_017  & Pollination & U.K. (England) & \citet{Memmott2002} \\
    M\_PL\_018  & Pollination & Denmark & Olesen, J. M. Unpublished.  \\
    M\_PL\_019  & Pollination & U.S.A. (Colorado) & \citet{Inouye1988}  \\
    M\_PL\_020  & Pollination & Canada (N.W.T.) & \citet{Kevan1970} \\
    M\_PL\_021  & Pollination & Japan (Kyoto) & \citet{Kato1990}  \\
    M\_PL\_022  & Pollination & Argentina (Mendoza) & \citet{Medan2002} \\
    M\_PL\_023  & Pollination & Argentina (Mendoza) & \citet{Medan2002} \\
    M\_PL\_024  & Pollination & Canada (N.W.T.) & \citet{Mosquin1967} \\
    M\_PL\_025  & Pollination & U.S.A. (North Carolina) & \citet{Motten1982}  \\
    M\_PL\_026  & Pollination & Ecuador (Gal\'{a}pagos Islands) & \citet{McMullen1993}  \\
    M\_PL\_027  & Pollination & New Zealand (South Island) & \citet{Primack1983} \\
    M\_PL\_028  & Pollination & New Zealand (South Island) & \citet{Primack1983} \\
    M\_PL\_029  & Pollination & New Zealand (South Island) & \citet{Primack1983} \\
    M\_PL\_030  & Pollination & Venezuela & \citet{Ramirez1992} \\
    M\_PL\_031  & Pollination & Venezuela & \citet{Ramirez1989} \\
    \hline
    \end{tabular}
    \end{center}
    \end{table}

@@

    \begin{table*}[h!]
    \begin{center}
    \begin{tabular}{|l l l m{6cm} |}
    \hline
    Network & Network type & Country & Original source \\
    \hline
    M\_PL\_032  & Pollination & U.S.A. (Illinois) & \citet{Schemske1978}  \\
    M\_PL\_033  & Pollination & Canada (Ontario) & \citet{Small1976} \\
    M\_PL\_034  & Pollination & Chile & \citet{SmithRamirez2005}  \\
    M\_PL\_035  & Pollination & Jamaica & \citet{Percival1974}  \\
    M\_PL\_036  & Pollination & Portugal (Azores) & Olesen, J. M. Unpublished.  \\
    M\_PL\_037  & Pollination & Denmark & \citet{Montero2005} \\
    M\_PL\_038  & Pollination & Denmark & \citet{Montero2005} \\
    M\_PL\_039  & Pollination & Spain (Canary Islands) & \citet{Stald2003} \\
    M\_PL\_040  & Pollination & Jamaica & \citet{Ingversen2006} \\
    M\_PL\_041  & Pollination & Dominica & \citet{Ingversen2006} \\
    M\_PL\_042  & Pollination & Ecuador (Gal\'{a}pagos Islands) & \citet{Philipp2006} \\
    M\_PL\_043  & Pollination & Denmark & \citet{Montero2005} \\
    M\_PL\_044  & Pollination & Japan (Amami Islands) & \citet{Kato2000}  \\
    M\_PL\_045  & Pollination & Denmark (Greenland) & \citet{Lundgren2005}  \\
    M\_PL\_046  & Pollination & Denmark & \citet{Bundgaard2003} \\
    M\_PL\_047  & Pollination & Denmark & \citet{Dupont2009a}  \\
    M\_PL\_048  & Pollination & Denmark & \citet{Dupont2009a}  \\
    M\_PL\_049  & Pollination & Denmark & \citet{Bek2006}  \\
    M\_PL\_050  & Pollination & Spain (Canary Islands) & \citet{Stald2003} \\
    M\_PL\_051  & Pollination & Argentina (R\'{i}o Negro) & \citet{Vazquez2002} \\
    M\_PL\_052  & Pollination & Denmark (Greenland) & \citet{Witt1998}  \\
    M\_PL\_053  & Pollination & Japan (Kyusu) & \citet{Yamazaki2003}  \\
    M\_PL\_054  & Pollination & Japan (Kyoto) & \citet{Kakutani1990}  \\
    M\_PL\_055  & Pollination & Japan (Fukui Prefacture) & \citet{Kato1996}  \\
    M\_PL\_056  & Pollination & Japan (Yamanashi) & \citet{Kato1993}  \\
    M\_PL\_057  & Pollination & Japan (Kibune) & \citet{Inoue1990} \\
    M\_PL\_058  & Pollination & Spain (Catalonia) & \citet{Bartomeus2008} \\
    M\_PL\_059  & Pollination & Brazil (Bu\'{i}que) & \citet{Bezerra2009} \\
    Basset  & Herbivory & Papua New Guinea & \citet{Basset1996}  \\
    Bl\"{u}thgen  & Herbivory & Malaysia (Sabah) & \citet{Bluthgen2006a}  \\
    Bodner  & Herbivory & Ecuador & \citet{Bodner2010}  \\
    Coley & Herbivory & Panama & \citet{Coley2006} \\
    Ibanez  & Herbivory & France (Central French Alps) & \citet{Ibanez2013}  \\
    Joern\_altuda  & Herbivory & U.S.A. (Texas) & \citet{Joern1979} \\
    Joern\_marathon  & Herbivory & U.S.A. (Texas) & \citet{Joern1979} \\
    Novotny & Herbivory & Papua New Guinea & \citet{Novotny2012} \\
    Peralta & Herbivory & New Zealand (South Island) & \citet{Peralta2016} \\
    Sheldon & Herbivory & U.S.A. (Washington) & \citet{Sheldon1978} \\
    Ueckert & Herbivory & U.S.A. (Colorado) & \citet{Ueckert1971} \\
    \hline
    \end{tabular}
    \end{center}
    \end{table*}
\clearpage
\newpage
